### 2017-02-27 R/ITHIM.Rmd
Added line to create sample trip file for Ali

```{r loadITHIM, message = FALSE, eval = TRUE, warning = FALSE, error = TRUE, echo = FALSE}
document("~/ITHIM/")
install("~/ITHIM/")
#install_github("syounkin/ITHIM", ref="cambridge")
install_github("smbache/magrittr", ref="master")

@@

```{r compute, echo = FALSE, eval = TRUE}
date()
compute <- FALSE
```

@@

NHTS <- merge(NHTS.person, NHTS.trips, by = c("HOUSEID","PERSONID"), all.x = TRUE)
NHTS <- within(NHTS, TRVL_MIN <- ifelse(is.na(TRVL_MIN), 0, TRVL_MIN))
saveRDS(NHTS, file = "./data/NHTS.rds")
```

>>>>

```{r loadITHIM, message = FALSE, eval = TRUE, warning = FALSE, error = TRUE, echo = FALSE}
document("~/ITHIM/")
install("~/ITHIM/")
#install_github("syounkin/ITHIM", ref="devel")
install_github("smbache/magrittr", ref="master")

@@

```{r compute, echo = FALSE, eval = TRUE}
date()
compute <- TRUE
```

@@

NHTS <- merge(NHTS.person, NHTS.trips, by = c("HOUSEID","PERSONID"), all.x = TRUE)
NHTS <- within(NHTS, TRVL_MIN <- ifelse(is.na(TRVL_MIN), 0, TRVL_MIN))
saveRDS(NHTS, file = "./data/NHTS.rds")

# write.csv(with(NHTS,data.frame(HOUSEID, PERSONID, SEX, AGE, MODE = AT, TRVL_MIN, TRPMILES)), file = "./misc/NHTS.csv", quote = FALSE, row.names = FALSE)
